%-------------------------
% Resume in Latex
% Author : Abey George
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}


\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    {\Huge \scshape Prasanna D} \\ \vspace{1pt}
    Dindigul,Tamilnadu,India. \\ \vspace{1pt}
    \small \href{tel:+918825525231}{ \raisebox{-0.1\height}\faPhone\ \underline{+91-8825525231} ~} \href{mailto:prasannatony12@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{prasannatony12@gmail.com}} ~ 
    \href{https://linkedin.com/in/prasanna-d-78a291211}{\raisebox{-0.2\height}\faLinkedinSquare\ \underline{prasanna-d-78a291211}}  ~
    \href{https://github.com/P-r-a-s-a-n-n-a}{\raisebox{-0.2\height}\faGithub\ \underline{P-r-a-s-a-n-n-a}} ~
\end{center}


%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {NPR College of Engineering and Technology}{Aug 2019 -- Jun 2023}
      {BE - ECE  - \textbf{CGPA} - \textbf{8.33(upto 7th Sem)}}{Natham, Dindigul.}
     
  \resumeSubHeadingListEnd
  \vspace{-12pt}
  
  \resumeSubHeadingListStart
    \resumeSubheading
      {Devangar Hr Sec School}{Jun 2018 -- Mar 2019}
      {HSC -   Bio Mathematics - \textbf{Percentage} - \textbf{76\%}}{Chinnalapatti, Dindigul}
  \resumeSubHeadingListEnd
  \vspace{-10pt}

   \resumeSubHeadingListStart
    \resumeSubheading
      {Devangar Hr Sec School}{Jun 2016 -- Mar 2017}
      {SSLC - \textbf{Percentage} - \textbf{94\%}}{Chinnalapatti, Dindigul}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{SKILLS}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-2pt, parsep=5pt]
                \item Web Developement
                \item Full Stack Developement
                \item App Development
                \item Artificial Intelligence
                \item Machine Learning
                \item Data Science
                \item Data Analyst
                \item Internet of Things
                \item UI
                \item Version Control
                \item Database Management Systems(DBMS)
                \item Web Servers and Deployment(CLOUD)
                \item Agile Methodologies
                \item Problem Solving and Troubleshooting
                \item Collabaration and Communication 
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


\vspace{5pt}
%-----------PROJECTS-----------
\section{PROJECTS}
    \vspace{-5pt}
    \resumeSubHeadingListStart
     \resumeProjectHeading
          {\href{ProjectLink.com}{\textbf{\large{\underline{Discord Web 3.0 Real-Time Decentralized Chat App}}} \href{https://codesandbox.io/s/covid-19-stats-r3zt3g}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{NextJS Blockchain Gun.js}}} {Present}
          \vspace{-10pt}
          \resumeItemListStart
            \resumeItem{\normalsize{Building a Web 3.0 Application with Next JS and styling app using Modular CSS.
            \textbf{}}}
            \resumeItem{\normalsize{Setup and run a decentralized database node with Gun.js and adding Web 3.0 authentication using MetaMask. \textbf{}}}
            \vspace{-10pt}
            \resumeItem{\normalsize{Storing the tweets and users in Sanity.io, deploy and host the app on Vercel Deploy and host the app on Vercel. \textbf{}}}
          \resumeItemListEnd 
          \vspace{-13pt}
          
     \resumeProjectHeading
          {\href{ProjectLink.com}{\textbf{\large{\underline{IoT Industry Waste Water Monitoring System}}} \href{https://github.com/P-r-a-s-a-n-n-a/IBM-Project-39637-1660472677} {\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{Blynk IBM Cloud ESP32 Picokit}}} {May 2023}
          \vspace{-10pt}
          \resumeItemListStart
            \resumeItem{\normalsize{Developed both hardware and software models for monitoring waste water through web application. \textbf{}}}
            \resumeItem{\normalsize{pH, Turbidity sensors collects water contamination and pH levels via ESP32 directly send it to the cloud. \textbf{}}}
            \resumeItem{\normalsize{Integrated IBM cloud used to monitored the data and web application. \textbf{}}}
             \resumeItem{\normalsize{Alerting the authorities if water quality its not good so they check and prevent the release of harmful water in the land. \textbf{}}}
            \resumeItem{\textcolor{accent} {\href{https://drive.google.com/file/d/1WvxKMzqRnrTflmfRnqCzqUcgSnp5AMBX/view?usp=sharing} {\underline{\normalsize{Download}}}}}
          \resumeItemListEnd
          \vspace{-13pt}
          
       \resumeProjectHeading
          {\href{ProjectLink.com}{\textbf{\large{\underline{Web Phishing Detection}}} \href{https://github.com/P-r-a-s-a-n-n-a/IBM-Project-42431-1660662531}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{Python Scikit-learn BeautifulSoup Pandas Flask IBM Cloud}}}{Feb 2023}
          \vspace{-10pt}
          \resumeItemListStart
            \resumeItem{\normalsize{Developed a demo website using Python,Flask with Machine learning predictive model. 
            \textbf{}}}
            \resumeItem{\normalsize{Explored a dataset(inputScript) to understand its structure using Pandas and necessary libraries for data analysis and data visualization.
            \textbf{}}}
            \resumeItem{\normalsize{Implemented the Machine Learning algorithms like Random Forest, Feature engineering, extraction to train the data and trained model tested using F1 Score.
            \textbf{}}}
            \resumeItem{\normalsize{Deployed it for real time web application and created an API end point for making predictions via IBM Watson Cloud platform.
            \textbf{}}}
            \resumeItem{\normalsize{Accomplished predictive model performance predictions outperformed with accuracy of 96.77 percentage in a real world settings.
            \textbf{}}}

            \resumeItem{\textcolor{accent} {\href{https://drive.google.com/file/d/149AHqIwRb9flSH8hNjFHoDUpJiWVzNtU/view?usp=share_link} {\underline{\normalsize{Demo Video}}}}}
          \resumeItemListEnd 
          \vspace{-13pt}
          
     
          
          \resumeProjectHeading
          {\href{ProjectLink.com}{\textbf{\large{\underline{Real Time Covid 19 Tracking Website}}} \href{https://codesandbox.io/s/covid-19-stats-r3zt3g}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{HTML5 CSS3 Javascript}}}{June 2022}
          \vspace{-10pt}
          \resumeItemListStart
            \resumeItem{\normalsize{Built a real time Responsive Website of Covid-19 stats using HTML, CSS, Javascript.  
            \textbf{}}}
            \resumeItem{\normalsize{JavaScript's fetch API can be employed to retrieve data from the API endpoints and update the website accordingly.  
            \textbf{}}}
            \resumeItem{\normalsize{Used jQuery, Chart.js for data manipulation and visualization including statistics like death,cases,recovered.  
            \textbf{}}}
            \resumeItem{\normalsize{Provided accurate and up-to-date information about the pandemic in an user friendly accessible.  
            \textbf{}}}
          \resumeItemListEnd 
          
    \resumeSubHeadingListEnd
\vspace{-12pt}

%


%-----------EXPERIENCE-----------
\section{INTERNSHIPS}
  \resumeSubHeadingListStart
     \resumeSubheading
      {Bharat Intern \href{https://drive.google.com/file/d/19HDIl2RmMmBgoy-umeJEsjZcxAJOgPcE/view?usp=drive_link}{\raisebox{-0.1\height}\faExternalLink }}{May 2023 -- Jun 2023} 
      {\underline{Data Science Intern}}{Remote}
      \resumeItemListStart
        \resumeItem{\normalsize{Demonstrated Long Short-Term Memory (LSTM) neural networks to predict stock prices. The data is loaded from a CSV file, preprocessed, split into training and testing sets, and an LSTM model is created using the TensorFlow library.}}
         \vspace{1pt}
          \resumeItem{\normalsize{ Predicted the survival outcome of passengers aboard the Titanic using machine learning techniques.Model selection is made using a Decision Tree classifier and Random Forest and XGBoost algorithms.
         \textbf{}}}
          \vspace{1pt}
          \resumeItem{\normalsize{Implemented of a neural network-based system for recognizing handwritten digits. It is trained on the MNIST dataset and evaluated on a test dataset.
 \textbf{}}}
  
      \resumeItemListEnd 

    \resumeSubheading
      {Tessolve \href{https://www.tessolve.com/}{\raisebox{-0.1\height}\faExternalLink }}{Jan 2023 -- Jun 2023} 
      {\underline{Embedded IoT Project Trainee}}{Remote}
       \vspace{1pt}
      \resumeItemListStart
        \resumeItem{\normalsize{Designed hardware kit for prenatal care. Integrated sensors, to collect vital signs data including heart rate, body temperature, fetal movements and kickcounts.}}
         \vspace{1pt}
          \resumeItem{\normalsize{Implemented a secure data transmission to transmit the collected health data from sensors to a cloud server for storage and analysis.
         \textbf{}}}
          \vspace{1pt}
          \resumeItem{\normalsize{Developed a user-friendly mobile interface using Blynk IoT for pregnant women to view their health data, receive personalized insights, and track their progress throughout the pregnancy.
 \textbf{}}}
  
      \resumeItemListEnd  
      \resumeSubheading
      {Spacescan \href{https://drive.google.com/file/d/1rvZ9M3CWzbueZ5GQBphy1yF2cC4VlREF/view?usp=drive_link}{\raisebox{-0.1\height}\faExternalLink }}{Mar 2022 -- Feb 2023} 
      {\underline{Junior Software Developer and Community Leader}}{Remote}
      \vspace{1pt}
      \resumeItemListStart
        \resumeItem{\normalsize{I honed my programming skills in JavaScript, ReactJS, NextJS, and API dB management. \textbf{}}}
        \vspace{1pt}
          \resumeItem{\normalsize{I have hands-on experience working with Object Oriented JavaScript (OOJS), JavaScript libraries, and ReactJS, NextJS, enabling me to build complex and interactive web applications.
 \textbf{}}}
 \vspace{1pt}
          \resumeItem{\normalsize{As a Community Leader, I have been responsible for creating content and search engine optimization(SEO) of website, overseeing the development of the company's online community.
 \textbf{}}}
  
      \resumeItemListEnd  
  \resumeSubHeadingListEnd
\vspace{-12pt}
%-----------PROGRAMMING SKILLS-----------
\section{TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\normalsize{Languages:}}{ \normalsize{Python, Javascript, C, SQL(Postgres,MySQL), Typescript, HTML/CSS }} \\
    \vspace{2pt}
     \textbf{\normalsize{Frameworks:}}{\normalsize{ Flask, React, NextJS, Node.js, Git, MongoDB, DBeaver, Truffle, Docusaurus, Material-UI, Bootstrap, FastAPI(RestAPI), Framer }} \\
\vspace{2pt}
     \textbf{\normalsize{Libraries:}}{\normalsize{ numPy, Pandas, Keras, Seaborn, Matplotlib, Tensorflow, Scikit-learn, Tableau }} \\
    }}
 \end{itemize}
 \vspace{-13pt}


%-----------INVOLVEMENT---------------
\section{ACHIEVEMENTS}
    \resumeSubHeadingListStart
        \resumeSubheading{Project on Web Phishing Detection \href{https://courses.ictacademy.skillsnetwork.site/certificates/20c6a6b70e7a480ba4114a1abcc4aa96} {\raisebox{-0.1\height}\faExternalLink } }
        {Feb 2023}{\underline{About}}{Remote}
            \vspace{1pt}
            \resumeItemListStart
                \resumeItem{\normalsize{Successfully finished my project and got secured first place in my domain applied data science provided by ICT Academy at IBM Nalaiya Thiran. \textbf{}}}
                \vspace{2pt}
                \resumeItem{\normalsize{Utilized machine learning algorithms, including random forest and gradient boosting, to train and optimize a predictive model for identifying phishing websites. \textbf{}}}
                \vspace{2pt}
                \resumeItem{\normalsize{Achieved an impressive accuracy rate of 96 percent in detecting and flagging potential phishing websites, significantly reducing the risk of cyber threats for end-users. \textbf{}}}
            \resumeItemListEnd
            
    \resumeSubheading{Presentation for TECHgium \href{https://drive.google.com/file/d/1xDHj6wnvC676K-z7R-MenoCu4KUbUCB5/view?usp=drive_link} {\raisebox{-0.1\height}\faExternalLink }        
    $|$ \large{\underline{VoxelNet TensorFlow OpenCV LiDAR}}} {Feb 2023}{\underline{About}}{Remote}
    \vspace{1pt}
            \resumeItemListStart
                \resumeItem{\normalsize{My idea  selected for presentation round in TECHgium challenge named Identifying a similarity pattern in a 3D LIDAR point cloud among 473 colleges around the world.\textbf{}}}
                \vspace{2pt}
                \resumeItem{\normalsize{Implemented VoxelNet algorithm used to End-to-End Learning for Point Cloud Based 3D Object Detection.\textbf{}}}
                \vspace{-10pt}
                \resumeItem{\normalsize{Experimented on KITTI dataset detection data shows VoxelNet outperforms the LiDAR based 3D detection methods by a large margin 81.97 and birds eye view detection by 89.60 percent.\textbf{}}}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
 \vspace{-10pt}
 
 %-----------CERTIFICATIONS---------------
 \section{CERTIFICATIONS}
 
$\sbullet[.75] \hspace{0.1cm}$ {Data Science using Python }{\href{https://www.pantechelearning.com/MAY23/PEL_NM_PARTDSA_663.pdf} {\raisebox{-0.1\height}\faExternalLink } $-$ \large{{TNSDC - Naan Mudhalvan - Pantech}} \hspace{1.7cm}\\
 \vspace{2pt}

$\sbullet[.75] \hspace{0.1cm}$ {Embedded systems with AI and IoT }{\href{https://drive.google.com/file/d/1vHHzB53UABYKYKE0eHIcSdxRWTuKqPvg/view?usp=drive_link} {\raisebox{-0.1\height}\faExternalLink } $-$ \large{{NSIC - Govt of India}} \hspace{1.7cm}\\
 \vspace{2pt}

$\sbullet[.75] \hspace{0.1cm}$ {AI for India  }{\href{https://www.guvi.in/verify-certificate?id=941y56i91j065hI47A} {\raisebox{-0.1\height}\faExternalLink } $-$ \large{{GUVI - IITM Research Park}} \hspace{1.7cm}\\
 \vspace{2pt}

$\sbullet[.75] \hspace{0.1cm}$ {Face Recognition App using Python }{\href{https://www.guvi.in/verify-certificateid=u8933f16214cK5tTqs#} {\raisebox{-0.1\height}\faExternalLink } $-$ \large{{GUVI - IITM Research Park}} \hspace{1.7cm}\\
 \vspace{2pt}

$\sbullet[.75] \hspace{0.1cm}$ {Responsive Web Design }{\href{https://freecodecamp.org/certification/fcc9b4c3c65-392b-4ac7-a770-b8a2c376b85c/responsive-web-design} {\raisebox{-0.1\height}\faExternalLink } $-$ \large{{freeCodeCamp}} \hspace{1.7cm}\\

\section{INTERESTS}

$\sbullet[.75] \hspace{0.1cm}$ {\href{certificateLink.com}{Web3}} \hspace{4.45cm}
$\sbullet[.75] \hspace{0.1cm}$ {\href{certificateLink.com}{Blockchain}} \hspace{4.5cm}
\vspace{2pt}
$\sbullet[.75] \hspace{0.2cm}${\href{certificateLink.com} {Data Science}}\\

$\sbullet[.75] \hspace{0.2cm}${\href{certificateLink.com}{Prompt Engineering}} \hspace{1.85cm}
\vspace{2pt}
$\sbullet[.75] \hspace{0.1cm}$ {\href{certificateLink.com}{AR - VR - Extended Reality}} \hspace{1.25cm}
$\sbullet[.75] \hspace{0.2cm}${\href{certificateLink.com}{Cross Platform Applications}} \\
 \vspace{2pt}
$\sbullet[.75] \hspace{0.2cm}${\href{certificateLink.com}{NFT - Metaverse Platforms}} \hspace{0.55cm}
 \vspace{2pt}
$\sbullet[.75] \hspace{0.2cm}${\href{certificateLink.com}{Digital Twin}} \hspace{4.15cm}
 \vspace{2pt}
$\sbullet[.75] \hspace{0.2cm}${\href{certificateLink.com}{Natural Language Processing}} \hspace{0.5cm}



 %-----------CERTIFICATIONS---------------
\section{LANGUAGES}

$\sbullet[.75] \hspace{0.1cm}$ {\href{certificateLink.com}{Tamil}} \hspace{4.45cm}
$\sbullet[.75] \hspace{0.1cm}$ {\href{certificateLink.com}{English}} \hspace{5.6cm}

\section{SUMMARY}
 \vspace{2pt}
$\sbullet[.75] \hspace{0.1cm}$ {I'm Prasanna, who has an insatiable\vspace{2pt} desire to learn and grow. I am an ECE graduate and am seeking an 
\vspace{2pt} opportunity where I can showcase my skills and provide value. Prasanna is a dynamic and tech-savvy enthusiast with a passion for the world of Web3, adept at leveraging cutting-edge technologies \vspace{2pt} to drive \vspace{2pt} transformational solutions.}
\vspace{5pt}

$\sbullet[.75] \hspace{0.1cm}$ {With a solid foundation as a developer, analyst, and engineer with expertise in javascript, python, AI \vspace{2pt} and \vspace{2pt} ML collaborative data science, web development, and full-stack and cloud applications to create immersive \vspace{2pt} user experiences and solve complex challenges. }
\vspace{5pt}

$\sbullet[.75] \hspace{0.1cm}$ {My collaborative mindset, strong problem-solving skills, and agile approach make me an ideal person \vspace{2pt} for driving impactful change in the digital realm. With a hunger for staying ahead of the learning curve and \vspace{2pt} a \vspace{2pt} commitment to pushing boundaries, I am poised to make productive waves in the tech industry and reshape \vspace{2pt} my future. }

\section{DECLARATION}
 \vspace{2pt}
$\sbullet[.75] \hspace{0.1cm}$ {I hereby declare that the information provided in this resume is true and accurate to the best of \vspace{2pt} my  \vspace{2pt} knowledge. I understand that any false statements or misrepresentations may result in disqualification from  \vspace{2pt} the hiring process or termination if employed. I am confident in my abilities and eager to contribute \vspace{2pt} my  \vspace{2pt} skills and expertise to make a meaningful impact in a challenging and dynamic work environment.

\end{document}
